|

### 2019-09-06 inst/manuscript/candidaev_supplement.Rmd
Track compressed supplementary .tiff files
Supplementary figure .tiff files with lzw compression are
a more manageable size, therefore track with git.

# arguments for figure S1 export
fS1_args <- list(tiff = list(type = "cairo"))
```

@@

# arguments for figure S2 export
fS2_args <- list(tiff = list(type = "cairo"))
```

>>>>

# arguments for figure S1 export
fS1_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

@@

# arguments for figure S2 export
fS2_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```
